flashscore by league

get the leagues I want

```{r}
library(tidyverse)
library(RSelenium)
```


```{r}
remDr <- remoteDriver(port = 4445L)
remDr$open(silent = TRUE)
```

look at soccer main page

```{r navigate}
my_url <- "https://www.flashscore.com/"
remDr$navigate(my_url)
title <- remDr$getTitle()
title
if (length(title) == 0) stop("no title") 
```

first skip the ad

```{r skip-ad}
Sys.sleep(1)
tryCatch(
  expr = {
    webElem <- remDr$findElement(using = "css", value = "#onetrust-accept-btn-handler")
    webElem$clickElement()
    print(remDr$getCurrentUrl())
    message("done successfully")
  },
  error = function(e) {
    message("Caught an error")
    print(e)
  },
  finally = {
    message("All done")
  }
)
```



```{r}
my_url <- "https://www.flashscore.com/football/albania/superliga/"
remDr$navigate(my_url)
```

```{r page-source}
my_html <- remDr$getPageSource()[[1]][1]
my_html %>% read_html() -> h
h
```

```{r}
h %>% html_node("#live-table > section:nth-child(2) > div.leagues--static.event--leagues.summary-results") -> lives
lives
```

need to look for "today's matches"

or get all the *leagues* in live, and make urls of them

- lowercase all
- replace spaces by dashes
- what about "name" with dashes in?
- maybe space-dash-space gets replaced by dash, but if championship group etc then not, it's the bit before the dash

```{r}
h %>% html_nodes("span") -> spans
spans %>% html_attr("class") -> classes
spans %>% html_attr("title") -> titles
spans %>% html_text() -> texts

tibble(class = classes, title = titles, text = texts) %>% 
  filter(str_detect(class, "event__title")) %>% 
  select(class, text) %>% 
  pivot_wider(names_from = "class", values_from = "text") %>% 
  rename(type = 1, name = 2) %>% 
  unnest_legacy(type, name)
```

or select from countries on left

find div ids in it

```{r}
lives %>% html_nodes("div") -> divs
divs %>% html_attr("id") -> ids
divs %>% html_attr("title") -> titles
tibble(id = ids, title = titles) %>% 
  drop_na(title, id)
```

get score and status also


livescore is also an option. No clicking on leagues to open them, matches have ids, but game info may be harder to extract






end

```{r}
remDr$close()
```

