---
title: "Grabbing rugby league scores from Flashscore using Selenium"
output: html_notebook
---

ok, that doesn't work either. Try `https://www.bbc.com/sport/rugby-league/scores-fixtures/2019-02-17` with date, back to Feb 3. Or, better, `https://www.rugby-league.com/2019_structure`, `https://www.rugby-league.com/championship__league_1/results`

## Packages

```{r}
library(tidyverse)
library(rvest)
library(RSelenium)
library(lubridate)
```

## Fire up Selenium and connect to current Flashscore rugby league page

```{bash}
docker stop quizzical_shannon
```


```{bash}
docker run -d -p 4445:4444 selenium/standalone-firefox
```

is it running?

```{bash}
docker ps
```

connect to it

```{r}
remdr <- RSelenium::remoteDriver(remoteServerAddr = "localhost",
                                 port = 4445L,
                                 browserName = "firefox")
remdr$open()
remdr$setTimeout(type = "page load", milliseconds = 10000)
```

the big loop

```{r}
my_url="https://www.flashscore.ca/rugby-league/"
remdr$navigate(my_url)
i=0
today=Sys.Date()
my_list=list()
repeat {
  # handle current day
  html_code=remdr$getPageSource()[[1]]
  html=read_html(html_code)
  html  
  the_date=today-i
  print(the_date)
  the_date_text=as.character(the_date)
  my_list[[the_date_text]]=tidy_results(html, the_date)
  i=i+1
  if (i>25) break
  # get yesterday
  element=remdr$findElement(using="css", "div.calendar__direction.calendar__direction--yesterday")
  element$clickElement()
  Sys.sleep(5)
  # then loop around again
}
my_list %>% bind_rows()
```



```{r}
my_url="https://www.flashscore.ca/rugby-league/"
remdr$navigate(my_url)
```

screenshot

```{r}
remdr$screenshot(display=T)
```

## grab current one

```{r}
html_code=remdr$getPageSource()[[1]]
html=read_html(html_code)
html
html %>% html_nodes('div') -> divs
divs %>% html_attr('class') -> classes
divs %>% html_text() -> texts
tibble(classes,texts) %>% 
  filter(str_detect(classes, "participant event") | str_detect(classes,"score event")) %>% 
  mutate(classes=str_replace(classes, " fontBold", "")) %>% 
  separate(classes, into=c("e1", "e2", "what"), sep="__") %>% 
  select(-e1, -e2) %>% 
  mutate(r=(row_number()+3) %/% 4) %>% # assumes 4
  spread(what, texts) %>% 
  mutate(s1=as.numeric(`score--home`), s2=as.numeric(`score--away`)) %>% 
  select(t1=`participant--home`, t2=`participant--away`, s1, s2)
```

my function from the other place:

```{r}
tidy_results=function(html,the_date) {
html %>% html_nodes('div') -> divs
divs %>% html_attr('class') -> classes
divs %>% html_text() -> texts
# check to see if I have anything I am looking for; if not, return empty df
tibble(classes,texts) %>% 
  filter(str_detect(classes, "participant event") | str_detect(classes,"score event")) %>% 
  mutate(classes=str_replace(classes, " fontBold", "")) %>% 
  separate(classes, into=c("e1", "e2", "what"), sep="__") %>% 
  select(-e1, -e2) %>% 
  mutate(r=(row_number()+3) %/% 4) %>% # assumes 4
  spread(what, texts) -> d
  if (nrow(d)==0) return(d)
  d %>% mutate(s1=as.numeric(`score--home`), s2=as.numeric(`score--away`), date=the_date) %>% 
  select(date, t1=`participant--home`, t2=`participant--away`, s1, s2)
}
```

```{r}
html_code=remdr$getPageSource()[[1]]
html=read_html(html_code)
tidy_results(html, Sys.Date())
```

find the thing to click for "yesterday":

```{r}
element=remdr$findElement(using="css", "div.calendar__direction.calendar__direction--yesterday")
element$clickElement()
Sys.sleep(5)
remdr$screenshot(display=TRUE)
```

```{r}
html_code=remdr$getPageSource()[[1]]
html=read_html(html_code)
tidy_results(html, Sys.Date()-1)
```


## the loop from the blog post

```{r}
gamelist=list()
i=0
remdr$navigate(url)
repeat {
  i=i+1
  html=remdr$getPageSource()[[1]]
  read_html(html) %>% 
    html_node(css="table") %>% 
    html_table() ->
  gamelist[[i]]
  if (i>=2) 
    if (identical(gamelist[[i]], gamelist[[i-1]])) 
      break
  element=remdr$findElement(using="css", "a.previous")
  element$clickElement()
  if (i>20) break
}
```

Have to get from today back. (Only access is via "yesterday".)

## References

[my blog post](http://ritsokiguess.site/docs/2018/09/01/scraping-icelandic-soccer-results-with-rvest-and-selenium/)