```{r package-connect}
library(tidyverse)
library(lubridate)
library(rvest)
library(glue)
library(janitor)
library(RSelenium)
remDr <- remoteDriver(port = 4445L)
remDr$open(silent = TRUE)
```

look at soccer main page

```{r navigate}
my_url <- "https://www.flashscore.com/"
remDr$navigate(my_url)
title <- remDr$getTitle()
title
if (length(title) == 0) stop("no title") 
```

copy function `get_game_info` from game_summary.Rmd


```{r}
get_text <- function(h, sel) {
  h %>% html_node(sel) %>% html_text()
}

goal_string <- function(h) {
  h %>% html_nodes("div") -> divs
  divs %>% html_attr("class") -> classes
  divs %>% html_text() -> texts
  
  # tibble(classes, texts) %>% View()
  
  i_want <- tribble(
    ~site_class, ~my_class,
    "smv__timeBox", "time",
    "smv__incidentHomeScore", "score",
    "smv__incidentAwayScore", "score"
  )
  
  tibble(classes, texts) %>% 
    filter(classes %in% i_want$site_class) %>% 
    left_join(i_want, by = c("classes"="site_class")) %>% 
    select(-classes) %>% 
    mutate(row = cumsum(my_class == "time")) %>% 
    pivot_wider(names_from = my_class, values_from = texts) -> d
  if (!("score" %in% names(d))) return("")
  d %>% drop_na(score) %>% 
    mutate(score = str_remove_all(score, " ")) %>% 
    mutate(goal = str_c(time, " ", score)) %>% 
    pull(goal) %>% 
    glue_collapse(sep = "; ")
}


get_game_info <- function(game_id, remDr) { # the game_id is the random string *without* the g_1_ on the front
  my_url <- "https://www.flashscore.com/"
  the_url = str_c(my_url, "match/", game_id, "/#/match-summary")
  print(the_url)
  remDr$navigate(the_url)
  Sys.sleep(1)
  my_html <- remDr$getPageSource()[[1]][1]
  my_html %>% read_html() -> h
  sel <- "#detail > div.duelParticipant > div.duelParticipant__home > div.participant__participantNameWrapper > div.participant__participantName.participant__overflow > a"
  home_team <- get_text(h, sel)
  sel <- "#detail > div.duelParticipant > div.duelParticipant__away > div.participant__participantNameWrapper > div.participant__participantName.participant__overflow > a"
  away_team <- get_text(h, sel)
  sel <- "#detail > div.tournamentHeader.tournamentHeaderDescription > div > span.tournamentHeader__country"
  league <- get_text(h, sel)
  sel <- "#detail > div.duelParticipant > div.duelParticipant__startTime > div"
  kickoff_utc <- get_text(h, sel)
  dt <- parse_date_time(kickoff_utc, orders = "dmyHM")
  kickoff <- with_tz(dt, tzone = "America/Toronto")
  sel <- "#detail > div.duelParticipant > div.duelParticipant__score > div > div.detailScore__wrapper"
  score <- get_text(h, sel)
  sel <- "#detail > div.duelParticipant > div.duelParticipant__score > div > div.detailScore__status"
  status <- get_text(h, sel)
  goals <- goal_string(h)
  tibble(kickoff, league, home_team, score, away_team, status, goals)
}
```


get the html ready to process

first skip the ad

```{r skip-ad}
Sys.sleep(1)
tryCatch(
  expr = {
    webElem <- remDr$findElement(using = "css", value = "#onetrust-accept-btn-handler")
    webElem$clickElement()
    print(remDr$getCurrentUrl())
    message("done successfully")
  },
  error = function(e) {
    message("Caught an error")
    print(e)
  },
  finally = {
    message("All done")
  }
)
```

```{r page-source}
my_html <- remDr$getPageSource()[[1]][1]
my_html %>% read_html() -> h
h
```

```{r}
to_keep <- tribble(
  ~class, ~class_me,
  "event__stage", "stage",
  "event__time", "ko",
  "event__score event__score--home", "home_score",
  "event__score event__score--away", "away_score"
  )
h %>% html_elements("#live-table > section > div > div") %>% 
  html_elements("div") -> divs
divs %>% html_attr("class") -> classes
divs %>% html_text() -> texts
divs %>% html_attr("id") -> ids
```



```{r}
tibble(class = classes, id = ids, text = texts) %>% 
  fill(id) %>% 
  mutate(league = ifelse(class == "event__titleBox", text, NA)) %>% 
  fill(league) %>% 
  mutate(keep_row = ifelse(class %in% to_keep$class, "yes", "no")) %>% 
  filter(keep_row == "yes") %>% 
  left_join(to_keep) %>% 
  select(id, class_me, text) %>% 
  pivot_wider(names_from = class_me, values_from = text) %>% 
  extract(id, into = "id", regex = "._._(.*)$") -> d
nrow(d)
```

if this has zero rows, stop here

write this one with timestamp

```{r}
fname <- str_c("flash_", make_clean_names(now()), ".rds")
write_rds(d, fname)
```


read the last two

```{r}
files <- list.files(pattern = "^flash_")
ff <- rev(files)
ff
i <- 1
j <- 2 # change this to 2
d <- read_rds(ff[i])
d_prev <- read_rds(ff[j])
```


if either d or d_prev have no rows, stop here

```{r}
if (nrow(d)==0) stop("No rows in d")
if (nrow(d_prev)==0) stop("No rows in d_prev")
```


the first one of the day will include games that are finished now but were not started when we last looked

```{r want}
d %>% left_join(d_prev, by = "id") %>% 
  filter(!is.na(stage.x)) %>%               # started / going / finished now
  filter((stage.x != stage.y) |
         is.na(stage.y)) %>%                # stage change or stage was missing before
  filter((home_score.x != home_score.y) |   # home score different,
           (away_score.x != away_score.y) | # or away score different,
           (stage.x == "Finished") |        # or is finished now,
           (str_detect(stage.x, "fter"))    # or ended after ET/pens
         ) %>% 
  select(id) -> d_now
nrow(d_now)
```

if this has zero rows, then stop here

```{r}
if (nrow(d_now) == 0) stop("No new scores")
```


get details for games that need to be gotten



https://www.flashscore.com/match/tl37O6rA/#/match-summary/match-summary

```{r details}
d_now %>% 
  rowwise() %>% 
  mutate(info = list(get_game_info(id, remDr))) -> d_got
d_got %>% unnest(info) %>% 
  select(id, kickoff, league:goals) -> d_updated
d_updated
```

compare with prev

```{r wanted}
label <- str_c("latest ", Sys.time())
d_updated %>% left_join(d_prev, by = "id") %>% 
  mutate(prev_score = str_c("(", home_score, "-", away_score, ")")) %>% 
  mutate(match = str_c(home_team, " - ", away_team)) %>% 
  mutate(score_plus = str_c(score, " ", prev_score)) %>% 
  select(kickoff, league, match, score = score_plus, status, goals) %>% 
  arrange(kickoff) %>% View(label)
```

```{r}
remDr$close()
```


how many games still going?

```{r still-going}
d %>% 
  drop_na(stage) %>% 
  filter(stage != "Finished") %>% 
  filter(!str_detect(stage, "fter")) %>% 
  filter(stage != "Postponed") %>% 
  filter(stage != "Cancelled") %>% 
  nrow()
```

